Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2012-01-31 Multiresolution_framework/ltx/manuscript.tex
minor edits

  \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')&=\mathbf E_{\boldsymbol \Theta'}\left[2\ln p(\mathbf X,\mathbf Y;\boldsymbol \Theta)\right] \nonumber \\
 &=\mathbf E_{\boldsymbol\Theta'}\left[\sum_{t=0}^{T-1}2\ln p(\mathbf y_{t+1}|\mathbf x_{t+1})+\sum_{t=0}^{T-1}2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta)

@@

\mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta)\right]+\mathrm{const.}

@@

where the constant term can be ignored as it is independent of the parameters. Under the condition that the state distribution is Gaussian --- ignoring the normalising term, $1/(2\pi)^{\frac{n_x}{2}}\mid\boldsymbol\Sigma_w\mid^{-\frac{1}{2}}$ --- the conditional distribution $p(\mathbf x_{t+1} | \mathbf x_{t};\boldsymbol\Theta)$ can be written as

@@

p(\mathbf x_{t+1} | \mathbf x_{t};\boldsymbol\Theta)=  \exp\left({-\frac{1}{2}\left(\mathbf x_{t+1}-\mathbf A\left(\boldsymbol\theta\right)\mathbf  x_t\right)^\top\boldsymbol\Sigma_w^{-1}\left(\mathbf x_{t+1}-\mathbf A\left(\boldsymbol\theta\right)\mathbf  x_t\right)}\right).

@@

2\ln p(\mathbf x_{t+1} , \mathbf y_{t+1};\boldsymbol\Theta)=&-\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf x_{t+1}+2\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf A( \boldsymbol\theta)\mathbf x_t\nonumber \\

@@

2\ln p(\mathbf x_{t+1}, \mathbf y_{t+1};\boldsymbol\Theta)=&\beta+2 T_s\varsigma\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\mathbf x_t \nonumber \\

@@

2\ln p(\mathbf x_{t+1}, \mathbf y_{t+1};\boldsymbol\Theta)&=\beta+2 T_s\varsigma\mathrm{tr} \left\lbrace \mathbf x_t\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\right\rbrace \nonumber \\

>>>>

  \mathcal Q(\boldsymbol \theta,\boldsymbol\theta')&=\mathbf E_{\boldsymbol \theta'}\left[2\ln p(\mathbf X,\mathbf Y;\boldsymbol \theta)\right] \nonumber \\
 &=\mathbf E_{\boldsymbol\theta'}\left[\sum_{t=0}^{T-1}2\ln p(\mathbf y_{t+1}|\mathbf x_{t+1})+\sum_{t=0}^{T-1}2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta)

@@

\mathcal Q(\boldsymbol \theta,\boldsymbol\theta')=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta)\right]+\mathrm{const.}

@@

where the constant term can be ignored as it is independent of the parameters. Under the condition that the state distribution is Gaussian --- ignoring the normalising term, $1/(2\pi)^{\frac{n_x}{2}}\mid\boldsymbol\Sigma_w\mid^{-\frac{1}{2}}$ --- the conditional distribution $p(\mathbf x_{t+1} | \mathbf x_{t};\boldsymbol\theta)$ can be written as

@@

p(\mathbf x_{t+1} | \mathbf x_{t};\boldsymbol\theta)=  \exp\left({-\frac{1}{2}\left(\mathbf x_{t+1}-\mathbf A\left(\boldsymbol\theta\right)\mathbf  x_t\right)^\top\boldsymbol\Sigma_w^{-1}\left(\mathbf x_{t+1}-\mathbf A\left(\boldsymbol\theta\right)\mathbf  x_t\right)}\right).

@@

2\ln p(\mathbf x_{t+1} , \mathbf y_{t+1};\boldsymbol\theta)=&-\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf x_{t+1}+2\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf A( \boldsymbol\theta)\mathbf x_t\nonumber \\

@@

2\ln p(\mathbf x_{t+1}, \mathbf y_{t+1};\boldsymbol\theta)=&\beta+2 T_s\varsigma\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\mathbf x_t \nonumber \\

@@

2\ln p(\mathbf x_{t+1}, \mathbf y_{t+1};\boldsymbol\theta)&=\beta+2 T_s\varsigma\mathrm{tr} \left\lbrace \mathbf x_t\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\right\rbrace \nonumber \\
